---
title: "Week_9_r_markdown"
output: html_document
---

This is an Rmarkdown document.  I can type whatever I want.

 *bold is two asteriks.  Make sure to put the asterisks on both sides*
 **italics is one asterik**

### pound signs make bigger font
## two pound signs would be larger than three pound signs
#how about one pound sign? Even bigger


To insert a code chunk: ctrl+alt+i

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
glimpse(storms)


library(viridis)


ggplot(data=storms)+
  geom_jitter(aes(x = as.factor(month), y = pressure, fill = wind), pch=21, alpha= .05) +
                scale_fill_viridis_c()+
                theme_bw()+
                labs(title = "Hurricane Pressure v Month", subtitle = "with Max wind speed", x = "Month")




```

Make sure to delete the install.package from my code
If I did echo = FALSE, it wouldn't show my code.  putting warning = False, and message = FALSE removes warnings and messages when it it made to an HTML

suppressPackagesStartupMessages(library(tidyverse)) will just show what package you used and will get rid of all the other startup messages


writing out equations in Rmarkdown:

If you want to write and equation: you put a $ on either side of it.

$\sum_{i=y}^n x_i$


```{r}

library(knitr)

kable(head(storms), caption = "Table using Kable")

htmlTable::htmlTable(head(storms))

#make an interactive table

DT::datatable(storms)

library(plotly)

ggplotly(ggplot(data=storms)+
  geom_jitter(aes(x = as.factor(month), y = pressure, fill = wind), pch=21, alpha= .05) +
                scale_fill_viridis_c()+
                theme_bw()+
                labs(title = "Hurricane Pressure v Month", subtitle = "with Max wind speed", x = "Month"))


```

The Kable and htmlTable lines created tables


creating a map:  There is code online for this

Rmardown's website it pretty good

```{r}

```




